R Notebook

### 2024-08-07 02_paper/02_study/01_fitbit paper/Submission/analysis_270423.Rmd
tabeleln und so

stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
                     type = "html",
                     caption = "Pre Teaching Phase",
                     dep.var.labels = "Slope",
                     # order = c(1, 2, 3),
                     # covariate.labels = c("Disruption Factor",
                     #                      "Confidence Factor",
                     #                      "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )

>>>>

stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4,
                     type = "latex",
                     caption = "Pre Teaching Phase",
                     dep.var.labels = "Slope",
                     # order = c(1, 2, 3),
                     # covariate.labels = c("Disruption Factor",
                     #                      "Confidence Factor",
                     #                      "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
